---
title: "DMP"
author: "Kristen Boysen"
date: "January 22, 2016"
output: html_document
---

##Data Management Plan 
#### For Climate Impacts, Environmental Informatics Project
####By Kristen Boysen and Juliano Palacios


##Types of Data

Data consists on a historical series (1980-2013) of octopus landings from both the Pacific and the Caribbean coasts of Mexico. The data is publish every year by Mexico’s Fisheries Agency, thus is considered official. We also include the value (in Mexican Pesos) of each year fishery. That data is also reported by the Mexican authorities and is considered to be official. Finally, we included the Oceanic Nino Index. Data was provided by the National Oceanic and Atmospheric Agency and can be reviewed here http://www.cpc.noaa.gov/products/analysis_monitoring/ensostuff/ensoyears.shtml.

The index determines the year by periods based on a threshold of +/- 0.5oC for the Oceanic Niño Index (ONI) [3 month running mean of ERSST.v4 SST anomalies in the Niño 3.4 region (5oN-5oS, 120o-170oW)]. 


##Data and Metadata Standards
Datasets need metadata to be usable. Think about what details (metadata) someone else would need to be able to use these files. For example, you may need a readme.txt file to explain variables, structure of the files, etc. Consider the following:

What contextual details (metadata) are needed to make the data you capture or collect meaningful?
What form will the metadata describing/documenting your data take?
How will you create or capture these details?
Which metadata standards will you use and why have you chosen them?


##Policies for access and sharing
Our data is 100% public. Data from landings and revenue was provided by the Mexican government and can be accessed at: http://goo.gl/qBaqRp .  The Oceanic Nino Index data is publicly available at the NOAA site http://goo.gl/b2aXSf


##Policies for provisions for re-use, re-distribution
Describe policies surrounding the re-use of your data – the EAR division is specifically interested in how soon you will make your data available. If you will not be making the data available for re-use immediately, explain why. Remember that EAR specifies that you must make your data available no later than two years after your research is complete. If there are other policy issues regarding data access and re-use (ethical or privacy issues, for instance) elaborate on them here. Consider these questions:

When will you make the data available?
Does the original data collector/creator/principal investigator retain the right to use the data before opening it up to wider use?
Will any permission restrictions need to be placed on the data?
How long will the original data collector/creator/principal investigator retain the right to use the data before making them available for wider distribution?
Are there any embargo periods for political/commercial/patent reasons? If so, give details.
Are there ethical and privacy issues? If so, how will these be resolved?
What have you done to comply with your obligations in your IRB Protocol?
Who will hold the intellectual property rights to the data and how might this affect data access?
What and who are the intended or foreseeable uses / users of the data?


##Plans for archiving and preservation of access

What is the long-term strategy for maintaining, curating and archiving the data?
Which archive/repository/database have you identified as a place to deposit data?
What procedures does your intended long-term data storage facility have in place for preservation and backup?
How long will/should data be kept beyond the life of the project?
What data will be preserved for the long-term?
What transformations will be necessary to prepare data for preservation / data sharing?
What metadata/ documentation will be submitted alongside the data or created on deposit/ transformation in order to make the data reusable?
What related information will be deposited?

#Octopus Landings data for Mexico

```{r}
Landings<- read.csv("Data/OctoLanding.csv")
summary(Landings)
```

### Clean the data, can we eliminate those columns that we won't need?

```{r Select}
library(dplyr)
Clean<- select(Landings, Year:ONI)
head(Clean)

```

### Filter, how many years presented landings over 15,000 tons?

```{r Filter}
filter(Clean, Total.Landings >= 15000)

#22 years presented more than 15,000 tons
```

### Group, what was the mean catch for El Nino, La Nina and Normal years?
```{r group_by}
Clean %>% group_by(ONI) %>% summarize(M_Pacific_Landings=mean(Pacific.Landings),sd=sd(Pacific.Landings)) 
