---
title: "DMP"
author: "Kristen Boysen"
date: "January 22, 2016"
output: html_document
---

##Data Management Plan 
#### For Climate Impacts, Environmental Informatics Project
####By Kristen Boysen and Juliano Palacios


##Types of Data

Data consists on a historical series (1980-2013) of octopus landings from both the Pacific and the Caribbean coasts of Mexico. The data is officially published every year by Mexico’s Fisheries Agency. We also include the value (in Mexican Pesos) of the fishery each year. That data is also reported by the Mexican authorities and is considered to be official. Finally, we included the Oceanic Nino Index. Data was provided by the National Oceanic and Atmospheric Agency and can be reviewed [here.](http://www.cpc.noaa.gov/products/analysis_monitoring/ensostuff/ensoyears.shtml)

The index determines the year by periods based on a threshold of +/- 0.5oC for the Oceanic Niño Index (ONI) [3 month running mean of ERSST.v4 SST anomalies in the Niño 3.4 region (5oN-5oS, 120o-170oW)]. 


##Data and Metadata Standards
As we include more data into this project, we will keep detailed metadata of where data was acquired, resolution of data, and any assumptions we may make to integrate each dataset. 


##Policies for access and sharing
Our data is 100% public. Data from landings and revenue was provided by the Mexican government and can be accessed at: http://goo.gl/qBaqRp .  The Oceanic Nino Index data is publicly available at the NOAA site http://goo.gl/b2aXSf


##Policies for provisions for re-use, re-distribution
All of results from our analyses will be available to the public from our github site, and all our data we use will be publically available. 


##Plans for archiving and preservation of access

This project will be completed as part of ESM 296: Informatics at the Bren School of Environmental Science & Management. If this project continues beyond the quarter, we will decide how best to transfer and store our data.

#Octopus Landings data for Mexico

```{r}
Landings<- read.csv("Data/OctoLanding.csv")
summary(Landings)
```

### Clean the data, can we eliminate those columns that we won't need?

```{r Select}
library(dplyr)
Clean<- select(Landings, Year:ONI) 
head(Clean)

```

### Filter, how many years presented landings over 15,000 tons?

```{r Filter}
filter(Clean, Total.Landings >= 15000)

#22 years presented more than 15,000 tons
```

### Group, what was the mean catch for El Nino, La Nina and Normal years?
```{r group_by}
Clean %>% group_by(ONI) %>% summarize(M_Pacific_Landings=mean(Pacific.Landings),sd=sd(Pacific.Landings)) 
```

###price of landings
What was the price each year and what is the average price of octopus? 
```{r}
mutate(Clean, price= Economic.Value/Total.Landings) %>% 
  na.omit %>% 
  summarise(mean(price))

##the average price/landing unit is 2,565 (not including years without economic value of the fishery). 
```

