---
title: "Package explanation"
author: "Juliano Palacios Abrantes"
date: "March 10, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressWarnings(library(dplyr))
suppressWarnings(library(knitr))
```

From a master data set, a selected number of values are randomly picked. For example, in the following table, we see 10 groups of 3 values. Each value was randomly selected from a general pool. Notice that the amount of groups and values are options in the function.
```{r Data explanation, eval=T, echo=F}
CSData <- read.csv("./Data/CSData.csv")
Data<- select(CSData, Target)
#Data Set#
#head(Data)

x <- data.frame(matrix(nrow = 3, ncol=10))

for (i in 1:10){
    #x[i] = sample(data[[column]],n)
    x[i] = sample(Data[,1],3)
}

x <- kable(x, caption = "Groups of randomlly selected values. Each group represents 3 values randomlly selected from a 51 observations data set.")
x 

```

Once groups are formed, the function will run a parametric on side t.test (or non parametric). The selection between those two statistical analysis is optional in the function. Confidence intervals (99%, 95% and 90%) are also options to take, however t.test and 95% are the default values. Finally, the function will ask you for a "truth value" to witch you are comparing your samples. For a 99% CI non-parametric t.test comparing to a truth value of 50 (mu=50), code looks something like this:

  if (test == "w.test" & ci == "0.99"){

    Score<- apply(x, 2, wilcox.test, alternative = "two.sided"...
    mu = 50, paired = FALSE, var.equal = FALSE, conf.level = 0.99)
}

Once the statistical tests are carried out, the function will arrange the tests in two groups: one with statistical p value >0.05 and one with statistical p value < 0.05. Finally, a table will be returned from the actual function.

```{r Psim example, echo=T,warning=FALSE}
library(psim)
Table<-psim(Data,1,5,60,100)
```

```{r Psim result, echo=F, warning=FALSE}
Table <- kable(Table, caption = "Results of psim from Citizen Science data unsing 5 socres per group. 100 groups compared to a truth value of 60")
Table
```